Selecting and ranking interesting pairs of cyclic temporal granularities

### 2020-12-16 paper/main.Rmd
paper folder update

# Behavior of raw distance measure

@@

To understand the behavior of raw MMPD for different parameters $nperm$ <number of permutations>, $n$ <sample size> ($n_x$, $n_f$ and combination), $D$ <different data set>, $l_x$<levels of x-axis>, $l_f$ <levels of facets>.

D1 - Design null: 
D2 - Design vary_f:
D3 - Design var_x:
B4 - Design vary_all:

## Effect of parameters of the distribution under null distribution

@@

@@

@@

## Choice of tuning parameters

@@

## Distribution across facet and x categories
<!-- ### Need for normalisation -->

@@

```{r hist-nx-nfacet}
knitr::include_graphics(here::here("simulations/result_report/hist_nxbyfacet.png"))
```

```{r dist-across-facets, fig.cap = "Distribution of $MMPD_{raw}$ for different facet levels are shown. The location of the distribution shifts rightwards implying that as the number of facets increase, it is more likely that a higher value of $MMPD_{raw}$ will be obtained."}
here::here()
knitr::include_graphics(here::here("simulations/result_report","nx_by_facet_raw.png"))
```

@@

```{r dist-across-x, fig.cap = "Distribution of $MMPD_{raw}$ for different x levels are shown. The scale of the distribution becomes less and less implying that as the number of x levels increase, it is more likely that a higher value of $MMPD_{raw}$ will be obtained as the spread of the distribution decreases. "}
knitr::include_graphics(here::here("simulations/result_report/","nfacet_by_nx_raw.png"))
```

@@

## Distribution across different sample size
## Distribution across different permutation size
## Distribution across normal and non-normal underlying distribution

@@

>>>>

# Behavior of raw wpd (weighted pairwise distances)

@@

We conduct simulations to understand the behavior of raw WPD for different parameters
$l_x$ (levels of x-axis), $l_f$ (levels of facets), $\lambda$ (tuning parameter), $\omega$ (increment in each panel design) $data$ (data sets), $sample-size$ (tuning parameter), $nsim$ (number of simulations), $nperm$ (number of permutations (might not need depending on if norm works) and designs  
$D_{null}$  (No difference in distribution)  
$D_{var_f}$ (Difference in distribution only across facets)  
$D_{var_x}$ (Difference in distribution only across x-axis)  
$D_{var_{all}}$ (Difference in distribution in both facets and x-axis)

## Location and scale of the distribution under null design

@@

### Normal Distribution

@@

### Gamma Distribution

@@

## Choice of tuning parameters and effect of different increments

@@

## Alternate designs

```{r lamba-omega-alternate-design}
knitr::include_graphics((here::here("simulations/result_report/wpd_alterate_designs.png")))
```

 Distribution across facet and x categories
<!-- ### Need for normalisation -->

@@

```{r hist-nx-nfacet, eval = FALSE}
knitr::include_graphics(here::here("simulations/result_report/hist_nxbyfacet.png"))
```

```{r dist-across-facets, fig.cap = "Distribution of $MMPD_{raw}$ for different facet levels are shown. The location of the distribution shifts rightwards implying that as the number of facets increase, it is more likely that a higher value of $MMPD_{raw}$ will be obtained.", eval = FALSE}
here::here()
knitr::include_graphics(here::here("simulations/result_report","nx_by_facet_raw.png"))
```

@@

```{r dist-across-x, fig.cap = "Distribution of $MMPD_{raw}$ for different x levels are shown. The scale of the distribution becomes less and less implying that as the number of x levels increase, it is more likely that a higher value of $MMPD_{raw}$ will be obtained as the spread of the distribution decreases. ", eval = FALSE}
knitr::include_graphics(here::here("simulations/result_report/","nfacet_by_nx_raw.png"))
```

@@

## Sample size
## Number of permutations

@@

```{r}
knitr::include_graphics(here::here("simulations/null_design/figs/normalised","gamma_ridge_nxbynfacet.png"))
```
